MCREX: Using Monte Carlo algorithms to achieve resiliency and performance at scale for linear and non-linear solver applications

### 2013-10-15 doc/proposal/emory/bio-benzi.tex
Moved documents into new mcrex repo.

%%---------------------------------------------------------------------------%%
%% benzi.tex
%%---------------------------------------------------------------------------%%

\subsection{Biographical Sketch for Michele Benzi}

% This section is not called out in the RFP, so it could be omitted if
% you are tight on space.
%\vspace*{-1ex}
\subsubsection*{Address}
\begin{tabular}{l}
  Department of Mathematics and Computer Science \\
  Emory University \\
  400 Dowman Drive \\
  Atlanta, GA 30322 \\
  Email: {\tt benzi@mathcs.emory.edu}
\end{tabular}

%%---------------------------------------------------------------------------%%

\vspace*{-1ex}
\subsubsection*{Education and Training}
\vspace*{-1ex}
\begin{tabbing}
  \hspace*{1ex}
  xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxx \= xxxxxxxxx \kill
  University of Bologna, Italy \> Mathematics \>  B.S., 1987 \\
  North Carolina State University \> Mathematics \> M.S., 1991 \\
  North Carolina State University \> Applied Mathematics \> Ph.D., 1993
\end{tabbing}

%%---------------------------------------------------------------------------%%

\vspace*{-3ex}
\subsubsection*{Research and Professional Experience}
\vspace*{-1ex}
\begin{tabbing}
  \hspace*{1ex} 
  %% 
  \= 2012 -- present \hspace*{2ex} \= Samuel Candler Dobbs Professor, Emory
  University\\
  %%
  \> 2006 -- 2012 \> Professor, Emory University\\ 
  %% 
  \> 2000 -- 2006 \> Associate Professor, Emory University \\
  %%
  \> 1998 -- 2000 \> Staff member, Scientific Computing Group, LANL \\ 
  %%
  \> 1997 -- 1998 \> Director-funded postdoctoral associate, Scientific 
  Computing Group, LANL\\
  %%
  \> 1996 -- 1997 \> Postdoctoral Researcher, Parallel Algorithms Group,
  CERFACS, Toulouse, France\\
  %%
  \> 1993 -- 1996 \>  Researcher, Department of Mathematics, University of Bologna,
  Italy
\end{tabbing}

%%---------------------------------------------------------------------------%%

\vspace*{-3ex}
\subsubsection*{Related Publications}
\begin{enumerate}
\parskip = -2pt

@@

\item S.~P.~Hamilton, M.~Benzi and J.~S.~Warsa, ``Negative-flux fixups in 
  discontinuous finite element $S_N$ transport'', 
  Proceedings of the International Conference on Mathematics, 
  Computational Methods \& Reactor Physics 2009 (M\&C 2009), 
  American Nuclear Society, Vol. 4 (2009), pp. 2529-2538, 
  Saratoga Springs, NY, 2009.

@@

\end{enumerate}

%%---------------------------------------------------------------------------%%

\vspace*{-3ex}
\subsubsection*{Synergistic Activities}
\vspace{-1ex}
%
\begin{enumerate}
  \parskip = -2pt
\item Chair, SIAM Activity Group on Linear Algebra (2010-present); 
\item Member of the SIAM Council (2009-present);
\item SIAM Fellow (Class of 2012); 
\item Program Committeee Co-chair, 2012 SIAM Applied Linear Conference
  (Valencia, Spain, June 18-22, 2012);
\item Program Committeee Co-chair, SIAM Annual Meeting (Minneapolis, MN, July
  9-13, 2012).
\item Editor-in-Charge, SISC Copper Mountain Special Issue (2012-present).
\end{enumerate}

%%---------------------------------------------------------------------------%%

\vspace*{-3ex}
\subsubsection*{Co-Authors and Collaborators (last 48 months)}
\vspace{-1ex}

@@

%%\vspace*{1ex}
\subsubsection*{Graduate and Postdoctoral Advisors and Advisees}
% List all advisors and advisees for the past 5 years
\vspace*{-1ex}
%%{\parindent 0.2in \narrower 
Advisors:
\begin{enumerate}
\item Wayne Joubert (Postdoc, LANL)
\item Iain Duff (Postdoc, CERFACS)
\item Carl Meyer (PhD, NCSU)
\end{enumerate} 
\vspace*{-1ex}
Advisees: 
\begin{enumerate}
\item Paola Boito (Postdoc) 
\item Bora Ucar (Postdoc) 
\item Jia Liu (PhD)
\item Nader Razouk (PhD)
\item Lauren Taralli (PhD)
\item Steven Hamilton (PhD)
\item Zhen Wang (PhD)
\item Christine Klymko (PhD)
\item Verena Kuhlemann (PhD)
\item Cheng-yi Zhang (PhD)
\end{enumerate}

\pagebreak
\endinput

%%---------------------------------------------------------------------------%%
%% end of benzi.tex
%%---------------------------------------------------------------------------%%

>>>>

% THIS MUST ALL FIT IN 2 PAGES

\subsubsection{Biographical Sketch for Michele Benzi}

% This section is not called out in the RFP, so it could be omitted if
% you are tight on space.
%\vspace*{-1ex}
\subsubsection*{Address}
\vspace*{-1ex}
\begin{tabular}{l}
  Department of Mathematics and Computer Science \\
  Emory University \\
  400 Dowman Drive \\
  Atlanta, GA 30322 \\
  Email: {\tt benzi@mathcs.emory.edu}
\end{tabular}

%\vspace*{-1ex}
\subsubsection*{Education and Training}
\vspace*{-1ex}
\vspace*{-2ex}
\begin{tabbing}
\hspace*{3em}  \= \\
\> Ph.D., 1993, Applied Mathematics, North Carolina State University \\
\> M.S., 1991,  Mathematics, North Carolina State University\\
\> B.S., 1987,  Mathematics, University of Bologna, Italy\\
\end{tabbing}
\vspace*{-4ex}

%\vspace*{-1ex}
\subsubsection*{Research and Professional Experience}
\vspace*{-1ex}
\vspace*{-2ex}
\begin{tabbing}
\hspace*{3em} \= \\
\> Samuel Candler Dobbs Professor (2012--present), Emory University \\ 
\> Professor (2006--present), Emory University\\ 
\> Associate Professor (2000--2006), Emory 
   University \\
\> Staff member (1998--2000), Scientific Computing Group, LANL \\ 
\> Director-funded postdoctoral associate (1997--1998), Scientific 
  Computing Group, LANL\\
\> Postdoctoral Researcher, Parallel Algorithms Group,
  CERFACS, Toulouse, France (1996--1997)\\
\> Researcher, Department of Mathematics, University of Bologna,
   Italy (1993--1996)\\
\end{tabbing}
\vspace*{-4ex}

%\vspace*{-1ex}
\subsubsection*{Publications} 
% List up to ten relevant publications.
%\vspace*{-1ex}
\begin{enumerate*}

@@

\item S.~P.~Hamilton, M.~Benzi and J.~S.~Warsa, ``Negative-flux fixups in 
discontinuous finite element S_N transport'', 
Proceedings of the International Conference on Mathematics, 
Computational Methods & Reactor Physics 2009 (M&C 2009), 
American Nuclear Society, Vol. 4 (2009), pp. 2529-2538, 
Saratoga Springs, NY, 2009.

@@

\end{enumerate*}

%\pagebreak

%\vspace*{-1ex}
\subsubsection*{Synergistic Activities} 
%\vspace*{-1ex}
\begin{enumerate*}
\item Chair, SIAM Activity Group on Linear Algebra (2010-present); 
\item Member
of the SIAM Council (2009-present); 
\item SIAM Fellow (Class of 2012); 
\item Program Committeee Co-chair,
2012 SIAM Applied Linear Conference (Valencia, Spain, June 18-22, 2012); 
\item Program Committeee Co-chair, SIAM Annual Meeting (Minneapolis, MN,
July 9-13, 2012).
\item Editor-in-Charge, SISC Copper Mountain Special Issue (2012-present).
\end{enumerate*}

%\vspace*{-1ex}
\subsubsection*{Collaborators and Co-editors}
% List Collaborators for the past 48 months and co-editors for the
% past 24 months.
\vspace*{-1ex}

@@

%%\vspace*{1ex}
\subsubsection*{Graduate and Postdoctoral Advisors and Advisees}
% List all advisors and advisees for the past 5 years
\vspace*{-1ex}
%%{\parindent 0.2in \narrower 
Advisors:
\begin{enumerate*}
\item Wayne Joubert (Postdoc, LANL)
\item Iain Duff (Postdoc, CERFACS)
\item Carl Meyer (PhD, NCSU)
\end{enumerate*} 
\vspace*{-1ex}
Advisees: 
\begin{enumerate*}
\item Paola Boito (Postdoc) 
\item Bora Ucar (Postdoc) 
\item Jia Liu (PhD)
\item Nader Razouk (PhD)
\item Lauren Taralli (PhD)
\item Steven Hamilton (PhD)
\item Zhen Wang (PhD)
\item Christine Klymko (PhD)
\item Verena Kuhlemann (PhD)
\item Cheng-yi Zhang (PhD)
\end{enumerate*}
